---
title: "Scooby-Doo"
author: "Sara Knight, Alexa Kraklau"
date: "2/23/2022"
output: github_document
---
access code: 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

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
library(readr)
library(extrafont)
library(infer)
```

In this course, we will:

**Import, manage, and clean data.**


This is one of my examples of loading data.
```{r load_scoobydoo_data}
scoobydoo <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-13/scoobydoo.csv')
```
*********************************************************************************************************************************************
I am wondering if we should only include the variables we used in project
*********************************************************************************************************************************************

| Header                        |  Description
|:------------------------------|:--------------------------------
|`index`                        | Index ordering based on Scoobypedia (dbl)
|`series_name`                  | Name of Series (char)
|`network`                      | TV Network TV series takes place in (char)
|`season`                       | Season of TV Series (char)
|`title`                        | Title of Show/Movie (char)
|`imbd`                         | Score on IMBD (char)
|`engagment`                    | Number of Reviews on IMBD (char)
|`date_aired`                   | Date aired in US (dbl)
|`run_time`                     | Run time in min (dbl)
|`format`                       | Type of media (char)
|`monster_name`                 | Name of monster (char)
|`monster_gender`               | Binary monster gender (char)
|`monster_type`                 | Monster type (char)
|`monster_subtype`              | Monster subtype (char)
|`monster_species`              | Monster species (char)
|`monster_real`                 | Was monster real (char)
|`monster_amount`               | Monster amount (dbl)
|`caught_fred`                  | Caught by Fred (char)
|`caught_daphnie`               | Caught by Daphnie (char)
|`caught_velma`                 | Caught by Velma (char)
|`caught_shaggy`                | Caught by Shaggy (char)
|`caught_scooby`                | Caught by Scooby (char)
|`captured_fred`                | Captured Fred (char)
|`captured_daphnie`             | Captured Daphnie (char)
|`captured_velma`               | Captured Velma (char)
|`captured_shaggy`              | Captured Shaggy (char)
|`captured_scooby`              | Captured Scooby (char)
|`unmask_fred`                  | Unmasked by Fred (char)
|`unmask_daphnie`               | Unmasked by Daphnie (char)
|`unmask_velma`                 | Unmasked by Velma (char)
|`unmask_shaggy`                | Unmasked by Shaggy (char)
|`unmask_scooby`                | Unmasked by Scooby (char)
|`snack_fred`                   | Snack eaten by Fred (char)
|`snack_daphnie`                | Snack eaten by Daphnie (char)
|`snack_velma`                  | Snack eaten by Velma (char)
|`snack_shaggy`                 | Snack eaten by Shaggy (char)
|`snack_scooby`                 | Snack eaten by Scooby (char)
|`unmask_other`                 | Unmasked by other (chat)
|`caught_other`                 | Caught by other (char)
|`caught_not`                   | Not caught (logical)
|`trap_work_first`              | Trap worked first time (char)
|`caught_shaggy`                | Caught by Shaggy (char)
|`setting_terrain`              | Setting type of terrain (char)
|`setting_country_state`        | Setting Country State (char)
|`suspect_amount`               | Suspect amount (dbl)
|`non_suspect`                  | Non suspect (char)
|`arrested`                     | Arrested (char)
|`culprit_name`                 | Culprit name (char)
|`culprit_gender`               | Culprit binary gender(char)
|`culprit_amount`               | Culprit amount (dbl)
|`motive`                       | Motive (char)
|`if_it_wasn't_for`             | Phrase at end the of the show (char)
|`door_gag`                     | Door gag happened (logical)
|`number_of_snacks`             | Number of snacks (char)
|`split_up`                     | Did they split up (char)
|`another_mystery`              | Another mystery (char)
|`set_a_trap`                   | Did they set a trap (char)
|`jeepers`                      | Times "Jeepers" said (char)
|`jinkies`                      | Times "Jinkies" said (char)
|`my_glasses`                   | Times "My glasses" said (char)
|`just_about_wrapped_up`        | Times "Just about wrapped up" said (char)
|`zoinks`                       | Times "Zoinks" said (char)
|`groovy`                       | Times "Groovy" said (char)
|`scooby_doo_where_are_you`     | Times "Scooby doo where are you" said (char)
|`rooby_rooby_roo`              | Times "Rooby rooby roo" said (char)
|`batman`                       | Batman in episode (logical)
|`scooby_dum`                   | Scooby Dum in episode (logical)
|`scrappy_do`                   | Scrappy Doo in episode (logical)
|`hex_girls`                    | Hex Girls in episode (logical)
|`blue_falcon`                  | Blue Falcon in episode (logical)
|`fred_va`                      | Fred voice actor (char)
|`daphnie_va`                   | Daphnie voice actor (char)
|`velma_va`                     | Velma voice actor (char)
|`shaggy_va`                    | Shaggy voice actor (char)
|`scooby_va`                    | Scooby voice actor (char)

*********************************************************************************************************************************************
We wanted to create a unique color palette for this project. We took two distict colors from each of the characters
including the Mystery Machine. We found their hexidecimal codes from a website. Then created a fuction for the colors.
*********************************************************************************************************************************************

```{r colors}
 scooby_gang_colors <- function(...) {
   palette <- c(`Shaggy Green` = "#B8BE19",
                   `Shaggy Red Brown` ="#A44138",
                   `Velma Orange` = "#F8991D",
                   `Velma Red` = "#C70C47",
                   `Daphne Green` = "#D0D61B",
                   `Daphne Dark Purple` = "#6352A3",
                   `Scooby Brown` = "#6A3400",
                   `Scooby Blue` = "#7BDB9",
                   `Fred Blue` ="#009DDC",
                   `Fred Orange`= "#F47920",
                   `Mystery Machine Green` = "#00CFD4", 
                   `Mystery Machine Blue` ="#00E304")
  cols <-c(...)
  
  if (is.null(cols))
    return(palette)
  
  palette[cols]
}
#scooby_gang_colors("Shaggy Green") This is to check to see if it worked
```
*********************************************************************************************************************************************
I found the way to create a custom color palette from this website:
https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2
*********************************************************************************************************************************************

```{r}
scoobycleaned<-scoobydoo[!(scoobydoo$monster_name=="NULL" & scoobydoo$monster_type=="NULL"),]

```

```{r for side by side bar graph}

caught_captured<-scoobydoo %>% 
  select(caught_fred:captured_scooby) %>% 
  pivot_longer(cols = everything(),
               names_to = c("action","character"),
               names_pattern = "(.*)_(.*)",
               values_to = "yes") %>% 
  filter(yes == "TRUE")

```

**Create graphical displays and numerical summaries of data for exploratory analysis and presentations.**

```{r side by side bar graph}
boxplot1 <- ggplot(data = caught_captured, aes(x = character, fill = action)) +
  geom_bar(stat = "count", position = position_dodge(), alpha = 1,) +
  scale_fill_manual(values=c("captured" = "#00CFD4",
                             "caught" = "#00E304"))


boxplot1 <- boxplot1 + labs(title = "Captured versus Caught for Each Character",
              subtitle = "Comparison of amount of episodes each character was \ncaptured by monster versus catching the monster",
              x = "Characters", y = "Number of Episodes",
              fill="Action",
              tag = "1") + theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5)) +
  theme(text=element_text(size=10,  family="Times New Roman", color= "#6352A3" ))

boxplot1
```
Write R programs for simulations from probability models and randomization-based experiments.
Use source documentation and other resources to troubleshoot and extend R programs.

*********************************************************************************************************************************************
This is my attempt a looking at all the places Mystery Inc has been.

Here I filter the data in order to make a smaller data frame just looking at the location of the episode.
We knew in order to get an acurate count of the locations We would have to turn each individual state into
the United States. Later on after I joined the data with the map data would have to change it to USA instead.
There was also a few miscellaneous one like Hong Kong that need to be changed to China.

Then w grouped them together to find the totals of each location. We saw that there we some fictional locations
and locations that were to vague to include, so we filtered them out. 

Finally we joined this new data set with mapdat and created a world map showing  all of the locations the Mystery
Machine has traveled.

This is also an example of creating a graphical display of the world with a 
gradient of how many episodes were in the country.
*********************************************************************************************************************************************
```{r}
scoobydoo_earth <- scoobydoo %>% 
  select(setting_country_state)
  
scoobydoo_earth[scoobydoo_earth == "United States"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Arizona"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "California"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Colorado"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Florida"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Georgia"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Hawaii"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Illinois"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Kentucky"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Kentukey"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Louisiana"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Massachusetts"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Mississippi"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Missouri"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Nevada"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New Jersey"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New Mexico"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New York"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "North Carolina"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Pennsylvania"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Ohio"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Rhode Island"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Tennessee"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Texas"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Vermont"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Washington"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Washington D.C."] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Wisconsin"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "England"] <- "UK"
scoobydoo_earth[scoobydoo_earth == "Scotland"] <- "UK"
scoobydoo_earth[scoobydoo_earth == "Hong Kong"] <- "China"
scoobydoo_earth[scoobydoo_earth == "Siam"] <- "Thailand"

scoobydoo_earth <- scoobydoo_earth %>% 
  group_by(setting_country_state) %>% 
  summarise(num_of_episodes = n()) %>% 
  select(setting_country_state, num_of_episodes) %>% 
  filter(setting_country_state != "Atlantis") %>% 
  filter(setting_country_state != "Bermuda Triangle") %>% 
  filter(setting_country_state != "Indian Reserve") %>%  # Too vague
  filter(setting_country_state != "Mars") %>% 
  filter(setting_country_state != "Moon") %>% 
  filter(setting_country_state != "Pre-Historic") %>% 
  filter(setting_country_state != "Space") %>% 
  filter(setting_country_state != "Africa") %>% # Africa is a continent
  filter(setting_country_state != "Caribean") %>% # Caribean is part of many countries
  filter(setting_country_state != "South America") %>% #South America is a continent
  filter(setting_country_state != "Tibet") #I don't know enough about the history of Tibet
  
names(scoobydoo_earth)[names(scoobydoo_earth) == "setting_country_state"] <- "region"

mapdata <- map_data("world")

mapdata <-left_join(mapdata, scoobydoo_earth, by = "region")

#mapdata1 <- mapdata %>% filter(!is.na(mapdata$num_of_episodes)) This was making it so I couldn't see all the countries and commenting it out fixed it.

map1 <- ggplot(mapdata, aes(x = long, y = lat, group = group))+
  geom_polygon(aes(fill = num_of_episodes), color = "black")
map1

scoobydoo_world_map <- map1 + scale_fill_gradient(name = "Number of Episodes", low = scooby_gang_colors("Mystery Machine Blue"), high = scooby_gang_colors("Mystery Machine Green"), na.value = "gray")+
  labs(title = "Mystery Inc Traveling Around the World",
       caption = "Excluded Places inclued: Atlantis, Bermuda Triangle, Mars, Moon, Pre-Historic, and Space", tag = "2")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      rect = element_blank())

scoobydoo_world_map
#This was an attempt to figure out where the two data frames weren't matching up
#in_scooby_not_in_real_world <- anti_join(scoobydoo_earth, mapdata, by = "region")

```
*********************************************************************************************************************************************
I used this (youtube video)[https://www.youtube.com/watch?v=AgWgPSZ7Gp0] to find out how to make the world map
*********************************************************************************************************************************************

```{r bootstrapping}
scooby_tv_tidy <- scoobydoo_tv %>% 
  select(index, imdb) %>% 
  filter( imdb != "NULL")

scooby_sample <- scooby_tv_tidy %>% 
  rep_sample_n(size = 50, replace = TRUE, reps = 1000)

scooby_sample <- as.data.frame(apply(scooby_sample, 2, as.numeric)) 

scoobyboot <- scooby_sample %>% 
  group_by(index) %>% 
  summarize(mean_imdb = mean(imdb))

scoobyboot
```


```{r graph bootstrapping}

ggplot(scoobyboot, aes(x = mean_imdb)) +
  geom_histogram(binwidth = .1, color = "#00CFD4", fill = "#F8991D") +
  labs(title = "Distribution of Sample Means from 1000 Resamples", x = "Sampled Mean IMDB", y = "Count", tag = "3")+
  theme(plot.title = element_text(hjust = 0.5))

```
*********************************************************************************************************************************************
We wanted to use more of the colors from the fuction and we decided to look at the catch phrases of the characters.

First we created a data set that contained all the times the catch phrases were used. We summed up the colums and found
out how many times the line was said and made a variable named after the character. Both Velma and Shaggy had two 
catch phrases so we added them up. We made another data set of just how many times each character used their catch phrase
and finally graphed them using bar graphs.
*********************************************************************************************************************************************

```{r catchphrases}
scoobydoo_cp <- scoobydoo %>% 
  select("another_mystery", "jeepers", "jinkies", "my_glasses", "zoinks","groovy","rooby_rooby_roo")

scoobydoo_cp[scoobydoo_cp == "NULL"] <- "0"

scoobydoo_cp[] <- lapply(scoobydoo_cp, as.numeric)

fred <- sum(scoobydoo_cp$another_mystery) 
daphne <- sum(scoobydoo_cp$jeepers)
velma1 <- sum(scoobydoo_cp$jinkies)
velma2 <- sum(scoobydoo_cp$my_glasses)
shaggy1 <- sum(scoobydoo_cp$zoinks)
shaggy2 <- sum(scoobydoo_cp$groovy)
scooby <- sum(scoobydoo_cp$rooby_rooby_roo)

velma <- sum(velma1,velma2)
shaggy <- sum(shaggy1,shaggy2)

character <- c("Fred", "Daphne", "Velma", "Shaggy", "Scooby")
catch_phrase <- c(fred, daphne, velma, shaggy, scooby)

gang_cp <- data.frame(character, catch_phrase)

ggplot(data = gang_cp)+
  geom_bar(mapping = aes(x = character, y = catch_phrase), stat = "identity")+
  scale_fill_manual(values =c("Fred" = scooby_gang_colors("Fred Blue"),
                              "Daphne" = scooby_gang_colors("Daphne Purple"),
                              "Velma" = scooby_gang_colors("Velma Orange"),
                              "Shaggy" =scooby_gang_colors("Shaggy Green"),
                              "Scooby" = scooby_gang_colors("Scooby Brown")))
```




