---
title: "Scooby-Doo"
author: "Sara Knight, Alexa Kraklau"
date: "2/23/2022"
output: github_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

l
```{r load_packages}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
library(extrafont)

```

```{r load_data}

scoobydoo <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-13/scoobydoo.csv')

```

```{r fonts}


```

**Trying to create a color palette for our project**
```{r colors}
 scooby_gang_colors <- function(...) {
   palette <- c(`Shaggy Green` = "#B8B#19",
                   `Shaggy Red Brown` ="#A44138",
                   `Velma Orange` = "#F8991D",
                   `Velma Red` = "#C70C47",
                   `Daphne Green` = "#D0D61B",
                   `Daphne Dark Purple` = "#6352A3",
                   `Scooby Brown` = "#6A3400",
                   `Scooby Blue` = "#7BDB9",
                   `Fred Blue` ="#009DDC",
                   `Fred Orange`= "#F47920",
                   `Mystery Machine Green` = "#00CFD4", 
                   `Mystery Machine Blue` ="#00E304")
  cols <-c(...)
  
  if (is.null(cols))
    return(palette)
  
  palette[cols]
}
#scooby_gang_colors("Shaggy Green")
```
https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2


```{r for side by side bar graph}

caught_captured<-scoobydoo %>% 
  select(caught_fred:captured_scooby) %>% 
  pivot_longer(cols = everything(),
               names_to = c("action","character"),
               names_pattern = "(.*)_(.*)",
               values_to = "yes") %>% 
  filter(yes == "TRUE")

```

```{r side by side bar graph}
boxplot1 <- ggplot(data = caught_captured, aes(x = character, fill = action)) +
  geom_bar(stat = "count", position = position_dodge(), alpha = 1,) +
  scale_fill_manual(values=c("captured" = "#00CFD4",
                             "caught" = "#00E304"))


boxplot1 <- boxplot1 + labs(title = "Captured versus Caught for Each Character",
              subtitle = "Comparison of amount of episodes each character was captured by monster versus catching the monster",
              x = "Characters", y = "Number of Episodes",
              fill="Action",
              tag = "1") +
  theme(text=element_text(size=10,  family="Arial", color= "purple"))

boxplot1
```

```{r}
scoobycleaned<-scoobydoo[!(scoobydoo$monster_name=="NULL" & scoobydoo$monster_type=="NULL"),]

```
| Header                        |  Description
|:------------------------------|:--------------------------------
|`index`                        | Index ordering based on Scoobypedia (dbl)
|`series_name`                  | Name of Series (char)
|`network`                      | TV Network TV series takes place in (char)
|`season`                       | Season of TV Series (char)
|`title`                        | Title of Show/Movie (char)
|`imbd`                         | Score on IMBD (char)
|`engagment`                    | Number of Reviews on IMBD (char)
|`date_aired`                   | Date aired in US (dbl)
|`run_time`                     | Run time in min (dbl)
|`format`                       | Type of media (char)
|`monster_name`                 | Name of monster (char)
|`monster_gender`               | Binary monster gender (char)
|`monster_type`                 | Monster type (char)
|`monster_subtype`              | Monster subtype (char)
|`monster_species`              | Monster species (char)
|`monster_real`                 | Was monster real (char)
|`monster_amount`               | Monster amount (dbl)
|`caught_fred`                  | Caught by Fred (char)
|`caught_daphnie`               | Caught by Daphnie (char)
|`caught_velma`                 | Caught by Velma (char)
|`caught_shaggy`                | Caught by Shaggy (char)
|`caught_scooby`                | Caught by Scooby (char)
|`captured_fred`                | Captured Fred (char)
|`captured_daphnie`             | Captured Daphnie (char)
|`captured_velma`               | Captured Velma (char)
|`captured_shaggy`              | Captured Shaggy (char)
|`captured_scooby`              | Captured Scooby (char)
|`unmask_fred`                  | Unmasked by Fred (char)
|`unmask_daphnie`               | Unmasked by Daphnie (char)
|`unmask_velma`                 | Unmasked by Velma (char)
|`unmask_shaggy`                | Unmasked by Shaggy (char)
|`unmask_scooby`                | Unmasked by Scooby (char)
|`snack_fred`                   | Snack eaten by Fred (char)
|`snack_daphnie`                | Snack eaten by Daphnie (char)
|`snack_velma`                  | Snack eaten by Velma (char)
|`snack_shaggy`                 | Snack eaten by Shaggy (char)
|`snack_scooby`                 | Snack eaten by Scooby (char)
|`unmask_other`                 | Unmasked by other (chat)
|`caught_other`                 | Caught by other (char)
|`caught_not`                   | Not caught (logical)
|`trap_work_first`              | Trap worked first time (char)
|`caught_shaggy`                | Caught by Shaggy (char)
|`setting_terrain`              | Setting type of terrain (char)
|`setting_country_state`        | Setting Country State (char)
|`suspect_amount`               | Suspect amount (dbl)
|`non_suspect`                  | Non suspect (char)
|`arrested`                     | Arrested (char)
|`culprit_name`                 | Culprit name (char)
|`culprit_gender`               | Culprit binary gender(char)
|`culprit_amount`               | Culprit amount (dbl)
|`motive`                       | Motive (char)
|`if_it_wasn't_for`             | Phrase at end the of the show (char)
|`door_gag`                     | Door gag happened (logical)
|`number_of_snacks`             | Number of snacks (char)
|`split_up`                     | Did they split up (char)
|`another_mystery`              | Another mystery (char)
|`set_a_trap`                   | Did they set a trap (char)
|`jeepers`                      | Times "Jeepers" said (char)
|`jinkies`                      | Times "Jinkies" said (char)
|`my_glasses`                   | Times "My glasses" said (char)
|`just_about_wrapped_up`        | Times "Just about wrapped up" said (char)
|`zoinks`                       | Times "Zoinks" said (char)
|`groovy`                       | Times "Groovy" said (char)
|`scooby_doo_where_are_you`     | Times "Scooby doo where are you" said (char)
|`rooby_rooby_roo`              | Times "Rooby rooby roo" said (char)
|`batman`                       | Batman in episode (logical)
|`scooby_dum`                   | Scooby Dum in episode (logical)
|`scrappy_do`                   | Scrappy Doo in episode (logical)
|`hex_girls`                    | Hex Girls in episode (logical)
|`blue_falcon`                  | Blue Falcon in episode (logical)
|`fred_va`                      | Fred voice actor (char)
|`daphnie_va`                   | Daphnie voice actor (char)
|`velma_va`                     | Velma voice actor (char)
|`shaggy_va`                    | Shaggy voice actor (char)
|`scooby_va`                    | Scooby voice actor (char)



```{r}
scoobycaught<-scoobydoo[!(scoobydoo$monster_name=="NULL" & scoobydoo$monster_type=="NULL"),] %>% 
  pivot_longer(
    cols = `caught_fred`:`caught_scooby`,
    names_to = "caught",
    values_to = "words"
  )
```

**Ideas**
1. color-coordinated
2. pull fonts from the internet
5. Keep the movies/ Get rid of the movies?
6. What do they mean by crossover?

**Questions**

1. How did the average running time of Scooby-Doo change?

```{r season vs. airtime}

scoobydoo %>% 
  ggplot(mapping = aes(x = season, y = run_time))+
    geom_boxplot()

```
What is up with season 2?

```{r season vs. imbd}

scoobydoo %>% 
  ggplot(mapping = aes(x = index, y = imdb))+
  geom_point()

```

At the very start it looks like they were highly rated. Then it almost stabilized a little. Finally all over the place. Where I would go next is how well are the movies rated compared to shows or crossovers.

```{r Monster caught by Fred}

scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = caught_fred))+
  geom_bar(stat = "identity", fill = "light blue")

```

This is just me playing around with color and trying to graph things. 

```{r Fred was captured}
scoobycleaned %>% 
    ggplot(mapping = aes(y = season, x = captured_fred))+
  geom_bar(stat = "identity", fill = "light blue")
```

Fred captures the monster only slightly more than getting caught. Get rid of null?

```{r Daphnie catches the monster}
scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = caught_daphnie))+
  geom_bar(stat = "identity", fill = "purple")
```
Daphnie almost never caught the monster.

```{r Daphnie caught by the monster}
scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = captured_daphnie))+
  geom_bar(stat = "identity", fill = "purple")
```
However she got caught less than I thought (I tried light purple and it didn't work)


```{r Velma caught the monster}

scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = caught_velma))+
  geom_bar(stat = "identity", fill = " dark orange")

```

Velma was a little more sucessful than Daphnie, but not much

```{r Velma got caught by the monster}
scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = captured_velma))+
  geom_bar(stat = "identity", fill = "dark orange")
```
Looks to close to Daphnie. (I couldn't use light orange)

```{r Shaggy caught the monster}
scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = caught_shaggy))+
  geom_bar(stat = "identity", fill = "light green")
```

Now I'm confused about what null would mean. My first thought would be the episodes where Shaggy wasn't in them, but that doesn't make sense.

```{r Shaggy caught by monster}
scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = captured_shaggy))+
  geom_bar(stat = "identity", fill = "light green")
```

Less than Velma and Daphnie, but more than Fred.

```{r Scooby caught the monster}
scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = caught_scooby))+
  geom_bar(stat = "identity", fill = "tan")
```

I'm kinda suprised, kinda not that Scooby caught the most monsters.

```{r Scooby caught by monster}
scoobycleaned %>% 
  ggplot(mapping = aes(y = season, x = captured_scooby))+
  geom_bar(stat = "identity", fill = "tan")
```

```{r bar graph}

ggplot(data=scoobydoo, aes(x=monster_real, fill=monster_real)) +
    geom_bar(colour="blue", stat="Count") +
    guides(fill=FALSE)

```

```{r}
ggplot(data = scoobydoo, aes(x = captured_scooby, y = season, fill = season)) +
  geom_bar(stat = "Identity", position = position_dodge(), alpha = 0.75) 
```


```{r}

```



This was me just messing around and trying to figure out some big questions we can explore.


```{r}
scoobydoo_tv <- scoobydoo %>% 
  filter(format == "TV Series")

scoobydoo_tv_segmented <- scoobydoo %>% 
  filter(format == "TV Series (segmented)")

scoobydoo_crossover <- scoobydoo %>%
  filter(format == "Crossover")

scoobydoo_movie <- scoobydoo %>% 
  filter(format == "Movie")
```

```{r filter_out_different_show}
scoobydoo_where_are_you <- scoobydoo %>% 
  filter(series_name == "Scooby Doo, Where Are You!")
scoobydoo_the_new_scoobydoo_movies <- scoobydoo_tv %>% 
  filter(series_name == "The New Scooby-Doo Movies")
the_scoobydoo_show <- scoobydoo %>% 
  filter(series_name == "The Scooby-Doo Show" )
scoobydoo_and_scrappydoo <- scoobydoo %>% 
  filter(series_name == "Scooby-Doo and Scrappy-Doo (first series)")
new_scoobydoo_and_scrappydoo_show <- scoobydoo %>% 
  filter(series_name == "The New Scooby and Scrappy Doo Show")
```


This is my attempt a looking at all the places Mystery Inc has been.

Here I filter the data in order to make a smaller data frame. Then I changed
data points points so I could join this data fram with another. Finally I 
filtered out the data points that weren't useful to making my map.

This is also an example of creating a graphical display of the world with a 
gradient of how many episodes were in the country.
```{r}
scoobydoo_earth <- scoobydoo %>% 
  select(setting_country_state)
scoobydoo_earth[scoobydoo_earth == "United States"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Arizona"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "California"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Colorado"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Florida"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Georgia"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Hawaii"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Illinois"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Kentucky"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Kentukey"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Louisiana"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Massachusetts"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Mississippi"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Missouri"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Nevada"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New Jersey"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New Mexico"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New York"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "North Carolina"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Pennsylvania"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Ohio"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Rhode Island"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Tennessee"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Texas"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Vermont"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Washington"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Washington D.C."] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Wisconsin"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "England"] <- "UK"
scoobydoo_earth[scoobydoo_earth == "Scotland"] <- "UK"
scoobydoo_earth[scoobydoo_earth == "Hong Kong"] <- "China"
scoobydoo_earth[scoobydoo_earth == "Siam"] <- "Thailand"
scoobydoo_earth <- scoobydoo_earth %>% 
  group_by(setting_country_state) %>% 
  summarise(num_of_episodes = n()) %>% 
  select(setting_country_state, num_of_episodes) %>% 
  filter(setting_country_state != "Atlantis") %>% 
  filter(setting_country_state != "Bermuda Triangle") %>% 
  filter(setting_country_state != "Indian Reserve") %>%  # Too vague
  filter(setting_country_state != "Mars") %>% 
  filter(setting_country_state != "Moon") %>% 
  filter(setting_country_state != "Pre-Historic") %>% 
  filter(setting_country_state != "Space") %>% 
  filter(setting_country_state != "Africa") %>% # Africa is a continent
  filter(setting_country_state != "Caribean") %>% # Caribean is part of many countries
  filter(setting_country_state != "South America") %>% #South America is a continent
  filter(setting_country_state != "Tibet") #I don't know enough about the history of Tibet
  
names(scoobydoo_earth)[names(scoobydoo_earth) == "setting_country_state"] <- "region"
mapdata <- map_data("world")
mapdata <-left_join(mapdata, scoobydoo_earth, by = "region")
#mapdata1 <- mapdata %>% filter(!is.na(mapdata$num_of_episodes)) This was making it so I couldn't see all the countries and commenting it out fixed it.
map1 <- ggplot(mapdata, aes(x = long, y = lat, group = group))+
  geom_polygon(aes(fill = num_of_episodes), color = "black")
map1
scoobydoo_world_map <- map1 + scale_fill_gradient(name = "Number of Episodes", low = scooby_gang_colors("Mystery Machine Blue"), high = scooby_gang_colors("Mystery Machine Green"), na.value = "gray")+
  labs(title = "Mystery Inc Traveling Around the World",
       caption = "Excluded Places inclued: Atlantis, Bermuda Triangle, Mars, Moon, Pre-Historic, and Space")+
  theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      rect = element_blank())
scoobydoo_world_map
#This was an attempt to figure out where the two data frames weren't matching up
#in_scooby_not_in_real_world <- anti_join(scoobydoo_earth, mapdata, by = "region")
```